Security on Networks

### 2013-05-15 paper/paper.tex
Changing url and pictures and stuff.

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[margin=1.25in]{geometry}

@@

Solving for a mixed strategy Nash Equilibrium in this context is $PPAD$ complete.\footnote{http://www.cs.berkeley.edu/~christos/papers/cacmDGP-2.pdf} This implies that for all practical purposes, solving for a Nash Equilibrium is computationally intractable, although little is known about the actual complexity of $PPAD$ in relation to $P$ and $NP$.\footnote{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=4031362}

@@

We begin by presenting the average infection probability $\hat{P}$ when the edge creation probability in Erdos Renyi is very small (we choose $p = 0.005$). Here the Erdos Renyi parameter is $np = 0.5$, which is below the threshold value for the existence of a giant component. Under this regime, the average infection probability $\hat{P}$ is very low for all protection levels (even a protection rate of $q = 0.05$).

@@

\begin{figure}
  \caption{Average Infection Rates for $np = 0.5 < 1$}
\end{figure}

When the Erdos Renyi parameter predicts the presence of a giant component, the average infection rate has a strong dependence on the protection rate. We use $np = 5 > 1$ which should produce a giant component with high probability, and simulate the resulting infection probabilities for various values of $q$. For low $q$, the average infection rate is incredibly high. For example, when $q = 0.05$, the average infection rate is $\hat{P} = 0.93$ with a standard deviation of $0.0103$.

However, as the protection rate increases, the average infection probability decreases almost linearly until about $q = 0.6$. Once $q = 0.6$, the positive externalities start to kick in and the average infection probability drops off more dramatically than the linear trend would predict. This can be attributed to the "network effect", or the extra benefit that everyone obtains from one person increasing their protection. Having higher $q$ will positively impact your neighbors because of the lower probability of you getting infected and thus transmitting to your neighbors.

\begin{figure}
  \caption{Average Infection Rates for $np = 5 > 1$}
\end{figure}

However, you must have enough connections in order for this network effect to become substantial. This is why the network effect does not manifest itself when there is no giant component. The figure below shows the network effect for different levels of $q$, where network effect $\nu$ is defined as follows:
\begin{eqnarray}
 \nu = 1 - q - \hat{P}
\end{eqnarray}

@@

\begin{figure}
  \caption{Network Effect in a Giant Component ($np = 5$)}
\end{figure}

@@

Showing the difficulty of the computation of $\tilde{P}_i$ in the non-dynamic model is now as simple as showing a reduction of the Two Terminal Problem, since it is $\# P$ complete as shown by Ball (1980).\footnote{http://onlinelibrary.wiley.com/doi/10.1002/net.3230100206/pdf}

>>>>

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{float}
\usepackage{hyperref}
\usepackage[margin=1.25in]{geometry}

@@

  Solving for a mixed strategy Nash Equilibrium in this context is $PPAD$ complete.\footnote{\url{http://www.cs.berkeley.edu/~christos/papers/cacmDGP-2.pdf}} This implies that for all practical purposes, solving for a Nash Equilibrium is computationally intractable, although little is known about the actual complexity of $PPAD$ in relation to $P$ and $NP$.\footnote{\url{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=4031362}}

@@

We begin by presenting the average infection probability $\hat{P}$ when the edge creation probability in Erdos Renyi is very small (we choose $p = 0.005$). Here the Erdos Renyi parameter is $np = 0.5$, which is below the threshold value for the existence of a giant component. Under this regime, the average infection probability $\hat{P}$ is very low for all protection levels (even a protection rate of $q = 0.05$), as seen in the simulation results from figure \ref{avg_prob_np05.fig}.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{avg_prob_np05.png}
  \caption{Average Infection Rates with No Giant Component $np = 0.5 < 1$}
  \label{avg_prob_np05.fig}
\end{figure}

When the Erdos Renyi parameter predicts the presence of a giant component, the average infection rate has a strong dependence on the protection rate. We use $np = 5 > 1$ which should produce a giant component with high probability, and simulate the resulting infection probabilities for various values of $q$. Figure \ref{avg_prob_np5.fig} shows the results from our simulations for $np = 5$. For low $q$, the average infection rate is incredibly high. For example, when $q = 0.05$, the average infection rate is $\hat{P} = 0.93$ with a standard deviation of $0.0103$.

As the protection rate increases, the average infection probability decreases almost linearly until about $q = 0.6$. Once $q = 0.6$, the positive externalities start to kick in and the average infection probability drops off more dramatically than the linear trend would predict. This can be attributed to the "network effect", or the extra benefit that everyone obtains from one person increasing their protection. Having higher $q$ will positively impact your neighbors because of the lower probability of you getting infected and thus transmitting to your neighbors.

\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{avg_prob_np5.png}
  \caption{Average Infection Rates with Giant Component $np = 5 > 1$}
  \label{avg_prob_np5.fig}
\end{figure}

However, you must have enough connections in order for this network effect to become substantial. This is why the network effect does not manifest itself when there is no giant component. Figure \ref{network_effects_np5.fig} shows the network effect for different levels of $q$, where network effect $\nu$ is defined as follows:
\begin{eqnarray}
 \nu = 1 - q - \hat{P}
\end{eqnarray}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{network_effects_np5.png}
  \caption{Network Effect in a Giant Component ($np = 5$)}
  \label{network_effects_np5.fig}
\end{figure}

@@

Showing the difficulty of the computation of $\tilde{P}_i$ in the non-dynamic model is now as simple as showing a reduction of the Two Terminal Problem, since it is $\# P$ complete as shown by Ball (1980).\footnote{\url{http://onlinelibrary.wiley.com/doi/10.1002/net.3230100206/pdf}}
